---
title: "Process data from the Face-Body Compound task"
author: "Ruud Hortensius (University of Glasgow)"
date: "26/02/2020"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
---

Script is sequentially to outline logic of steps

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(fs) #install.packages("fs")
library(psycho) #install.packages("psycho")
library(tidyverse) #install.packages("tidyverse")
#install.packages("devtools")
#devtools::install_github("thomasp85/patchwork")
library(patchwork)
```

## Importing and wrangling data

Load the data stored in /data
Check: sub 15 24 27

```{r data, warning=FALSE}
DF <- dir_ls("data/", regexp = "\\.csv$") %>% #get all the csv files in the data folder
  #map_dfr(read.delim, sep = ",", header = TRUE) %>% #read in the data
  map_dfr(read_csv, col_types = cols("image.stopped" = col_character(), text.started = col_character(),  frameRate = col_character(), text_10.started = col_character())) %>%
  select("participant", "impar_incluso", "condsFile", "Body", "Face", "Type", "Gender", "CAfear", "CAanger", "key_resp_2.keys", "key_resp_2.rt") %>% #select the relevant columns
  filter(!is.na(key_resp_2.rt)) %>% #remove the instruction responses 
  rename("rt"= key_resp_2.rt, "resp" = key_resp_2.keys, "task" = condsFile) %>% #give responses and task a logical name
  mutate(session = str_match(participant,"A|B"), order = str_match(participant,"inc|imp"), group = str_match(participant,"E|C"), participant = str_remove_all(participant, "[:alpha:]")) %>% #get group, order and session
  mutate(task = str_match(task,"fear|anger")) %>% #remove .xlsx from the name
  mutate_all(str_to_lower) #%>% #only use lower case, easier to have conditional statements
  #mutate_at(vars(-rt),as.factor) %>% #change to factor
  #mutate(rt = as.numeric(rt)) #change to numeric

summary(DF)
```

Get the correct response pairing (q and p)
```{r keys}
DF <- DF %>%
  mutate_all(na_if,"")   %>% #before we can do fill "" need to be NA
  group_by(participant, group, session) %>%  #group by participant, group, session, because we want to do per individual
  mutate(CAfear = as.character(CAfear), CAanger = as.character(CAanger))  %>% #remove the factors
  fill(CAfear, .direction = "down") %>% #fill the CAfear column
  fill(CAanger, .direction = "down") %>% #fill the CAangry column
  mutate(HappyF = ifelse(CAfear == "q", "p", "q"), HappyA = ifelse(CAanger == "q", "p", "q")) #create the CAhappy column seperately for the fear/anger tasks
```

## Get accuracy

Calculate the correct response per trial
```{r ca}
DF <- DF %>%
  mutate(CA = ifelse(Face == "fear" & task == "fear", CAfear, ifelse(Face == "happy" & task == "fear", HappyF, ifelse(Face == "anger" & task == "anger", CAanger, HappyA)))) #get CA for the tasks
```

Calculate the accuracy
```{r acc}
DF <- DF %>%
  mutate(acc = ifelse(CA == resp, 1, 0))
```

Plot accuracy
```{r plot}
DF%>% group_by(participant, group, session, task, Gender) %>% 
  summarise(acc = mean(acc)) %>% 
  ggplot(., aes(x = group, y = acc, fill=Gender)) +
  geom_point(aes(colour = Gender), size = .5, shape = 20)+
  geom_boxplot(aes(x=group,y=acc),position=position_nudge(x = .1, y = 0),outlier.shape = NA, alpha = .5, width = .1, colour = "black")+ 
  ylim(0,1)+
  theme_classic() + 
  facet_wrap(task~session) + 
  ggtitle(paste("Accuracy per task and session"))
```

## Calculate Signal Detection indices

1. Calculate hits, false alarms, misses, and correction rejections 
```{r SDT}
DF <- DF %>%
  group_by(participant, group, session, task, Gender) %>% 
  mutate(h = ifelse(Face == task & acc == 1, 1, 0)) %>% # calculate hits
  mutate(m = ifelse(Face == task & acc == 0, 1, 0)) %>% # calculate misses
  mutate(cr= ifelse(Face != task & acc == 1, 1, 0)) %>% # calculate correct rejections
  mutate(fa= ifelse(Face != task & acc == 0, 1, 0)) # calculate false alarms
```

2. Summarise hits, false alarms, misses, and correction rejections (collapsed across distractor)
```{r hits and more}
DF <- DF %>%
  group_by(participant, group, session, task, Gender) %>% 
  summarise(h = sum(h),
            m = sum(m),
            cr = sum(cr),
            fa = sum(fa))
```

3. Calculate SDT indices (d' and c')
```{r dprime and more}
DF.SDT <- psycho::dprime(DF$h, DF$fa, DF$m, DF$cr)
DF <- cbind(DF, DF.SDT)
```

4. Plot the d' per task and session
```{r plot dprime}
DF %>% group_by(participant, group, session, task, Gender) %>% 
  ggplot(., aes(group, dprime, fill=Gender)) +
  geom_point(aes(colour = Gender), size = .5, shape = 20)+
  geom_boxplot(aes(x=group,y=dprime),position=position_nudge(x = .1, y = 0),outlier.shape = NA, alpha = .5, width = .1, colour = "black")+ 
  ylim(0,5)+
  theme_classic() +
  facet_wrap(task~session) + 
  ggtitle(paste("d' per task and session"))
```

5. Plot the c per task and session
```{r plot bias}
DF %>% group_by(participant, group, session, task, Gender) %>% 
  ggplot(., aes(group, c, fill=Gender)) +
  geom_point(aes(colour = Gender), size = .5, shape = 20)+
  geom_boxplot(aes(x=group,y=c),position=position_nudge(x = .1, y = 0),outlier.shape = NA, alpha = .5, width = .1, colour = "black")+ 
  theme_classic() +
  facet_wrap(task~session) + 
  ggtitle(paste("c per task and session"))
```

## Calculate d' and c following Snodgrass and Corwin (1988), as in Seinfeld et al. (2018)

1. Calculate H' and FA'

H' = (h + 0.5) / (h + m +1)
FA' = (f + 0.5) / (f + cr + 1)

```{r H and FA SC}
DF$cH <- (DF$h + 0.5) / (DF$h + DF$m +1)
DF$cFA <- (DF$fa + 0.5) / (DF$fa + DF$cr + 1)
```

2. Calculate dprime and C
```{r SDT SC}
DF$SCdprime <- qnorm(DF$cH)-qnorm(DF$cFA)
DF$SCc <- (qnorm(DF$cH)+qnorm(DF$cFA))*-.5
```

3. Plot correlation between measures

The two methods converge or more precisely the way psych calculates the D-prime and c is exactly similar to the one I used for Seinfeld et al. (2018)

For dprime
```{r comparison dprime}
plot(DF$SCdprime, DF$dprime)
```

For bias
```{r comparison bias}
plot(DF$SCc, DF$c)
```

## Plot the effect of Gender as in Seinfeld et al. (2018)

Plot the d' per task, session, and gender

1. Calculate the difference

```{r difference}
DF.diff <- DF %>%
  select(participant, group, session, task, Gender, dprime, c) %>%
  pivot_wider(names_from = session, values_from = c(dprime,c)) %>%
  mutate(dprime_diff = dprime_b - dprime_a, c_diff = c_b - c_a) %>%
  select(participant, group, task, Gender, dprime_diff, c_diff)
```

1. dprime
```{r plot dprime_diff}
d <- DF.diff %>% group_by(participant, group, task, Gender) %>% 
  ggplot(., aes(group, dprime_diff, fill=group)) +
  geom_point(aes(colour = group), size = .5, shape = 20)+
  geom_boxplot(aes(x=group,y=dprime_diff),position=position_nudge(x = .1, y = 0),outlier.shape = NA, alpha = .5, width = .1, colour = "black")+ 
  ylim(0,5)+
  theme_classic() +
  facet_wrap(task~Gender) + 
  ggtitle(paste("d' difference"))
```

2. c
```{r plot c_diff}
c <- DF.diff %>% group_by(participant, group, task, Gender) %>% 
  ggplot(., aes(group, c_diff, fill=group)) +
  geom_point(aes(colour = group), size = .5, shape = 20)+
  geom_boxplot(aes(x=group,y=c_diff),position=position_nudge(x = .1, y = 0),outlier.shape = NA, alpha = .5, width = .1, colour = "black")+ 
  theme_classic() +
  facet_wrap(task~Gender) + 
  ggtitle(paste("bias difference"))
```

```{r dprime gender}
d | c
```

## Next: Bayesian stats